---
title: "Company Reputation Poll Eda"
author: "Object of Type Closure is not Subsettable Group"
date: '2022-06-19'
output: html_document

knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../"
    )
  })
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(tidyverse)
library(ggplot2)
library(factoextra)
library(janitor)
library(here)
library(reactable)
library(tidyverse)
library(skimr)
library(ggbump)
library(tidyr)
library(cowplot)
library(wesanderson)
library(hrbrthemes)
library(dplyr)
library(viridis)
library(forcats)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Using a simple R script, the dataset is explored to present the most interesting and useful insights along with the questions they answer in a report format.


# Data
This data is the result of a partnership between Axios and Harris Poll to gauge the reputation of the most visible brands in America, based on 20 years of Harris Poll research.

- Methodology: The Axios Harris Poll 100 is based on a survey of 33,096 Americans in a nationally representative sample conducted March 11-April 3, 2022. The two-step process starts fresh each year by surveying the public’s top-of-mind awareness of companies that either excel or falter in society.

These 100 “most visible companies” are then ranked by a second group of Americans across the seven key dimensions of reputation to arrive at the ranking. If a company is not on the list, it did not reach a critical level of visibility to be measured

### Data Dictionary

# `poll.csv`

|variable  |class     |description |
|:---------|:---------|:-----------|
|company   |character | Company Name |
|industry  |character | Industry group |
|2022_rank |integer   | 2022 Rank (1 is better than 100) |
|2022_rq   |double    | 2022 RQ score. An RQ score is calculated by:  [ (Sum of ratings of each of the 9 attributes)/(the total number of attributes answered x 7) ]  x 100. Score ranges: 80 & above: Excellent; 75-79: Very Good ; 70-74: Good ; 65-69: Fair ; 55-64: Poor ; 50-54: Very Poor ; Below 50: Critical |
|change    |integer   | Change in rank from 2021         |
|year      |integer   | Year for that rank/RQ |
|rank      |integer   | Rank corresponding to the year|
|rq        |double    | RQ score corresponding to the year |

# `reputation.csv`
- All ranks in this for current year only

|variable  |class     |description |
|:---------|:---------|:-----------|
|company   |character | Company Name |
|industry  |character | Industry group |
|name      |character | Name of reputation category (P&S = Product and Service) |
|score     |double    | Score for reputation category |
|rank      |integer   | Rank for reputation category |



### Basic Information
```{r, echo = FALSE, message=FALSE}
# Get the Data

poll <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-31/poll.csv')
reputation <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-05-31/reputation.csv')

```


```{r , echo = FALSE}
reactable(poll)
```

```{r}
summary(poll)
```

By looking at Q1 and Q3 values we can observe the range of some metrics of the sample

# Poll EDA

```{r}

```


```{r , echo = FALSE}
reactable(reputation)
```

```{r}
summary(reputation)
```

By looking at Q1 and Q3 values we can observe the range of some metrics of the sample

# Reputation EDA

```{r}

```




